\begin{thebibliography}{}
%\small
%\setlength{\itemsep}{.25mm}

\bibitem{boulier:03IJF}
Bryan L. Boulier and H. O. Stekler
\newblock {\em Predicting the outcomes of National Football League games}.
\newblock International Journal of Forecasting, 19(2):257-270, 2003


\bibitem{Brier:BrierScore}
G.~W. Brier
\newblock {\em Verification of forecasts expressed in probabilities}.
\newblock Montly Weather Review, 78:1-3, 1950


\bibitem{huang06GeneralizedBradleyTerryModels}
T.~K. Huang and R.~C. Weng and C.~J. Lin
\newblock {\em Generalized {B}radley-{T}erry Models and Multi-Class Probability Estimates}.
\newblock Journal of Machine Learning Research, 7:85-115, 2006

\bibitem{neal03SliceSampling}
R.~M. Neal
\newblock {\em Slice sampling}.
\newblock The Annals of Statistics, 31(3):705-767, 2003.

\bibitem{Baio:10JAS}
G.~Baio and M.~A.~Blangiardo
\newblock {\em Bayesian hierarchical model for the prediction of football results}.
\newblock JOURNAL OF APPLIED STATISTICS, 37(2):253-264, 2010.

\bibitem{Abramowitz74HandbookOfMathematical}
M.~Abramowitz and I.~A. Stegun.
\newblock {\em Handbook of Mathematical Functions, With Formulas, Graphs, and
  Mathematical Tables}.
\newblock Dover Publications, New York, 1974.

\bibitem{birlutiu07ExpectationPropagation}
A.~Birlutiu and T.~Heskes.
\newblock Expectation propagation for rating players in sports competitions.
\newblock In {\em ECML-PKDD}, volume 4702 of {\em LNCS}, pages
  374--381. Springer, 2007.

\bibitem{dangauthier07337}
P.~Dangauthier, R.~Herbrich, T.~Minka, and T.~Graepel.
\newblock Trueskill through time: Revisiting the history of chess.
\newblock In {\em NIPS}, pages 337--344. MIT
  Press, Cambridge, MA, 2008.

\bibitem{elo78TheRatingOfChessPlayers}
A.~E. Elo.
\newblock {\em The rating of chess players: past and present}.
\newblock Arco Publishing, New York, 1978.

\bibitem{herbrich06569}
R.~Herbrich, T.~Minka, and T.~Graepel.
\newblock Trueskill$^{TM}$: A {B}ayesian skill rating system.
\newblock In {\em NIPS}, pages 569--576, 2006.

\bibitem{karlis09BayesianModellingFootballOutcomes}
D.~Karlis and I.~Ntzoufras.
\newblock Bayesian modelling of football outcomes: using the skellam's
  distribution for the goal difference.
\newblock {\em IMA Journal of Management Mathematics}, 20(2):133--145, 2009.

\bibitem{kschischang01498}
F.~R. Kschischang, B.~J. Frey, and H.~A. Loeliger.
\newblock Factor graphs and the sum-product algorithm.
\newblock {\em IEEE Transactions on Information Theory}, 47(2):498--519,
  February 2001.

\bibitem{minka01ExpectationUAI}
T.~Minka.
\newblock Expectation propagation for approximate bayesian inference.
\newblock In {\em UAI}, pages
  362--369. Morgan Kaufmann, 2001.

%\bibitem{thomasMinka2001}
%T.~Minka.
%\newblock {\em A family of algorithms for approximate {B}ayesian inference}.
%\newblock PhD thesis, MIT, 2001.

% \bibitem{thomasMinka2001}
% T.~Minka.
% \newblock {\em A family of algorithms for approximate {B}ayesian inference}.
% \newblock PhD thesis, Department of Electrical Engineering and Computer
%   Science, MIT, January 2001.

\bibitem{Moroney56FactsFromFigures}
M.~J. Moroney.
\newblock {\em Facts from figures}.
\newblock Penguin Press Science, 3rd edition, 1956.

\bibitem{Skellam46TheFrequencyDistribution}
J.~G. Skellam.
\newblock The frequency distribution of the difference between two
{P}oisson variates belonging to different populations.
\newblock {\em Journal of the Royal Statistical Society: Series A}, 109(3):296,
  1946.

\bibitem{Glickman98JASA}
M.~E. Glickman, and H.~S. Stern.
\newblock A state-space model for football league scores.
\newblock {\em Journal of the American Statistical Association}, 93(441):25--35,
  1998.

\bibitem{Beal:EMFixedPoint02}
M.~J. Beal, and Z.~Ghahramani.
\newblock The Variational {B}ayesian {EM} Algorithm for Incomplete Data: with
	Application to Scoring Graphical Model Structures.
\newblock {\em Proceedings of the Seventh Valencia International Meeting}: 453--464,
2002.

\bibitem{karlis09BayesianModellingFootballOutcomes}
D.~Karlis and I.~Ntzoufras,
\newblock Bayesian modelling of football outcomes: using the {S}kellam's distribution
	for the goal difference,
\newblock {\em IMA Journal of Management Mathematics}, 20(2):133--145, 2009.

\bibitem{Karlis03AnalysisOfSportsData}
D.~Karlis and I.~Ntzoufras,
\newblock Analysis of Sports Data by Using Bivariate {P}oisson Models,
\newblock {\em Journal of the Royal Statistical Society: Series D}, 52(3):381-393, 2003.

\bibitem{Moroney56FactsFromFigures}
M.~J. Moroney
\newblock Facts from figures,
\newblock Penguin Press Science, 3rd, 1956.

\bibitem{dixon97ModellingAssociationFootball}
M.~J. Dixon and S.~G. Coles,
\newblock Modelling Association Football Scores and Inefficiencies in the Football Betting Market,
\newblock {\em Journal of the Royal Statistical Society: Series C}, 46(2):265--280, 1997.

\bibitem{Guo:ECML2012}
S.~Guo and S.~Sanner and T.~Graepel and W.~Buntine
\newblock {\em Score-based Bayesian Skill Learning}.
\newblock Proceedings of the European Conference on Machine Learning and Principles
	and Practice of Knowledge Discovery in Databases, 106-121, 2012


\bibitem{Murray:AISTATS2010}
I.~Murray and R.~P. Adams and D.~J.C. MacKay
\newblock {\em Elliptical slice sampling}.
\newblock Proceedings of the 13th International Conference on Artificial Intelligence
	and Statistics, 541-548, 2010
	
%\bibitem{Maragakis08JCP}
%P.~Maragakis and F.~Ritort and C.~Bustamante and M.~Karplus and G.~E.~Crooks
%\newblock Bayesian estimates of free energies from nonequilibrium work data in the presence of instrument noise,
%\newblock {\em Journal of Chemical Physics}, 129(2), 2008.
\end{thebibliography}